Effects

### 2020-01-06 doc/Effects.Rmd
cleaned total.sc script, wont overwrite MLH1 Rdata

#load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/MLH1/MLH1_data_setup_12.20.19.RData")#fixing bugs, formating
load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/total_SC_30.12.19.RData")#total SC data

>>>>

#clean up total SC
load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/total_SC_1.6.20.RData")#total SC data

#load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/MLH1/MLH1_data_setup_12.20.19.RData")#fixing bugs, formating
#load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/total_SC_30.12.19.RData")#total SC data
